### 2018-02-23 Sections/collision_handling_and_classical_errors.tex
Crypto stuff minor

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

>>>>

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely unknown quantum state and prepare an identical copy of it. That is, there is no quantum process implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if it is restricted to a particular basis or subject to other constraints.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

### 2018-02-23 Sections/cryptowars.tex
Crypto stuff minor

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend attack\index{Intercept-resend attack} (or man-in-the-middle attack) may be detected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time-pad cipher\index{One-time-pad cipher}, presenting us with true information-theoretic security\index{Information-theoretic security}.

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{\cite{??? example companies}}. The main drawback is thus the ability to perform long-distance transmission of photons. For these reasons, current QKD networks have been limited to relatively small distances, on the order of $\sim100$km, including in Austria, Switzerland, Japan, USA, and China \cite{bib:lo2014secure}. The longest distance QKD network that is currently planned is the Beijing to Shanghai QKD link spanning a distance of $\sim2,000$km. This involves 32 trusted nodes\index{Trusted nodes} to break the total distance into shorter segments to convert the quantum information to classical information.

@@

The ready realisability of space based QKD was already noted in a variety of configurations including ground-to-space\index{Ground-to-space communication} and space-to-ground\index{Space-to-ground communication} quantum communication \cite{bib:rarity2002ground, bib:aspelmeyer2003long}. In the context of security, the first long-distance experiments that are likely to be demonstrated will employ trusted nodes\index{Trusted nodes}. For example, after performing QKD between satellite\index{Satellites} and ground stations, a satellite could store the key for some time until another QKD can be performed to another ground station\index{Ground stations} using a one-time pad\index{One-time pad cipher} \cite{bib:liao2017satellite}. These types of experiments are planned to eventually perform intercontinental QKD\index{Intercontinental QKD} between China and Austria.

@@

The two original QKD protocols, known as the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 protocol}, and \textit{E91} \cite{bib:Ekert91}\index{E91 protocol} protocols, are based on polarisation encoding in photons. BB84 requires only the transmission of a sequence of single photons, polarisation-encoded\index{Polarisation encoding} with random data. E91, on the other hand, requires a server that distributes entangled Bell-pairs between Alice and Bob. Since then, numerous other protocols for QKD have been proposed, for example, using CV (continuous variable) states\index{Continuous variable QKD}.

The BB84 protocol is described in detail in Alg.~\ref{alg:bb84}. Suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. By sacrificing a some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Thus, Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time-pad\index{One-time-pad protocol}.

@@

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day technology.

@@

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84.

@@

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms. The protocol is information-theoretically secure\index{Information-theoretic security}, and therefore no physically realisable computer, even a quantum computer, can compromise it. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers, that are employed to attack other encryption protocols, do not compromise QKD.

@@

As discussed above, the RSA public-key cryptosystem is vulnerable to an efficient quantum attack, whereas private-key schemes like AES are not (believed to be). Thus, combining QKD schemes with private-key classical schemes does not compromise security in the quantum era.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \ket{\mathrm{GHZ}}$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

@@

>>>>

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend attack\index{Intercept-resend attack} (or man-in-the-middle attack) may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time-pad cipher\index{One-time-pad cipher}, presenting us with true information-theoretic security\index{Information-theoretic security}.

The central notion to QKD protocols, in their numerous manifestations, is that measurement of quantum states invokes a wavefunction collapse. When measuring a state in a basis for which that state is not an eigenstate, this necessarily changes the state. QKD relies on this simple result from quantum mechanics to reveal any eavesdropper performing an intercept-resend attack\index{Intercept-resend attack} via the changes to transmitted quantum states that this would induce.

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{\cite{??? example companies}}. The main drawback is thus the ability to perform long-distance transmission of photons. Current QKD networks have been limited to relatively small distances, on the order of $\sim100$km, including in Austria, Switzerland, Japan, USA, and China \cite{bib:lo2014secure}. The longest distance QKD network that is currently planned is the Beijing to Shanghai QKD link, spanning a distance of $\sim2,000$km. This involves 32 trusted nodes\index{Trusted nodes} to break the full route into shorter segments.

@@

The ready realisability of space based QKD was already noted in a variety of configurations including ground-to-space\index{Ground-to-space communication} and space-to-ground\index{Space-to-ground communication} quantum communication \cite{bib:rarity2002ground, bib:aspelmeyer2003long}. In the context of security, the first long-distance experiments that are likely to be demonstrated will employ trusted nodes\index{Trusted nodes}. For example, after performing QKD between satellite\index{Satellites} and ground stations\index{Ground stations}, a satellite could store the key for some time in a quantum memory\index{Quantum memory} until another QKD can be performed to another ground station using a one-time pad\index{One-time pad cipher} \cite{bib:liao2017satellite}. These types of experiments are currently planned to eventually facilitate intercontinental QKD\index{Intercontinental QKD} between China and Austria.

@@

The first described QKD scheme was the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 protocol} protocol, which exploits the fact that states encoded in the 0/1-basis but measured in the $\pm$-basis (and vice versa) collapse randomly, yielding completely random measurement outcomes, whereas states measured in the same basis in which they were encoded always correctly communicate a single bit of information.

Implemented photonically, BB84 requires only the transmission of a sequence of single photons, polarisation-encoded\index{Polarisation encoding} with random data.

The BB84 protocol is described in detail in Alg.~\ref{alg:bb84} in the context of polarisation-encoded photons, which is the most natural (but not only) setting for this protocol.

@@

To understand the secrecy of the protocol, suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of encoding bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. Thus, by sacrificing some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Now Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time-pad\index{One-time-pad protocol} with perfect secrecy.

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day photonics technology. The scheme has been adapted to physical architectures beyond just polarisation-encoded photons, such as CV encodings\index{Continuous variable QKD} \cite{???}.

@@

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared, random bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84.

@@

%
% Continuous Variable Protocols
%

\paragraph{Continuous variable protocols}

\comment{To do. Zixin perhaps??}

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms. The protocols are information-theoretically secure\index{Information-theoretic security}, and therefore no physically realisable computer, even a quantum computer, can compromise them. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers\index{Integer factorisation}, that are employed to attack other encryption protocols, do not compromise QKD.

@@

As discussed, the RSA public-key cryptosystem is vulnerable to an efficient quantum attack, whereas private-key schemes like AES are not (believed to be). Thus, combining QKD schemes with private-key classical schemes does not compromise security in the quantum era.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n}+\ket{1}^{\otimes n})$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

@@

\comment{Attackes based on bad implementation rather than bad theory}

### 2018-02-23 Sections/entanglement_the_ultimate_quantum_resource.tex
Crypto stuff minor

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell-pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theory} limitations.
\item Photonic Bell-pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell-pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{UDP}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell-pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

>>>>

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell-pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell-pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell-pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{UDP}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell-pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

### 2018-02-23 Sections/network_algorithms.tex
Colour-coded tables
Crypto stuff minor

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin)& with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search algorithm}\index{Depth-first-search algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

The first proven shortest-path algorithm was by Dijkstra \cite{bib:Dijkstra59}, which requires runtime,
\begin{align}
	O(|V|^2),
\end{align}
also residing in \textbf{P}\index{\textbf{P} \& \textbf{BPP}}. Subsequently, a number of improvements and variations on Dijkstra's algorithm have been proposed, most notably the $A^*$ algorithm \cite{bib:Astar}\index{$A*$ algorithm}, which has found widespread modern use, using a heuristic approach to improve performance over Dijkstra.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loopStart)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}). \comment{Fix me}} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search algorithm}\index{Depth-first-search algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

The first proven shortest-path algorithm was by Dijkstra \cite{bib:Dijkstra59}, which requires runtime,
\begin{align}
	O(|V|^2),
\end{align}
also residing in \textbf{P}\index{\textbf{P} \& \textbf{BPP}}. Subsequently, a number of improvements and variations on Dijkstra's algorithm have been proposed, most notably the $A^*$ algorithm \cite{bib:Astar}\index{Shortest-path algorithm}, which has found widespread modern use, using a heuristic approach to improve performance over Dijkstra.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}). \comment{Fix me}} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

### 2018-02-23 Sections/protocols_for_the_quantum_internet.tex
Crypto stuff minor

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using: two-level\index{Two-level atoms} or $\lambda$-configuration atoms\index{$\lambda$-configuration atoms}; superconducting rings\index{Superconducting rings}; ion traps\index{Ion traps}; atomic ensembles\index{Atomic ensembles}; and countless more.

>>>>

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using: two-level\index{Two-level atoms} or $\lambda$-configuration atoms\index{$\lambda$-configuration systems}; superconducting rings\index{Superconducting rings}; ion traps\index{Ion traps}; atomic ensembles\index{Atomic ensembles}; and countless more.
